MSB1015_Assignment 2

### 2019-09-28 MSB1015_Assignment2_SuzannetenHage.Rmd
Update MSB1015_Assignment2_SuzannetenHage.Rmd
Fixed a bug: I forgot to create a data structure containing both the predictors and boiling points. This is fixed now.

#Reformatting of smiles into correct format for CDK. Kekulise checks for electrons, and prevents parsing of incorrect smiles. 
parsed_smiles <- parse.smiles(data_raw$smiles, kekulise=TRUE)

#Determine which descriptors to get. 
descNames <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor')

#Get descriptors
descriptors <- eval.desc(parsed_smiles, descNames)

@@

#Find all rownumbers of the values in Celcius. 
celcius <-  which(grepl('degree Celsius', data_raw$bpUnitLabel))
for (i in 1:length(celcius)) {
  #Convert the value to kelvin
  data_raw$bp[celcius[i]] <- data_raw$bp[celcius[i]] + 273.15
  #Convert the label to kelvin. 
  data_raw$bpUnitLabel[celcius[i]] <- 'kelvin'
}

#Find all rownumbers of the values in Fahrenheit. 
fahrenheit <- which(grepl('degree Fahrenheit', data_raw$bpUnitLabel))
for (i in 1:length(fahrenheit)) {
  #Convert the value to kelvin
  data_raw$bp[fahrenheit[i]] <- (data_raw$bp[fahrenheit[i]] + 459.67) * (5/9)
  #Convert the label to kelvin. 
  data_raw$bpUnitLabel[fahrenheit[i]] <- 'kelvin'
}

@@

3b) Normalization of the data.

```{r} 
#Normalization of data
data <- data.frame(descriptors, data_raw$bp)

#Devide every column by its maximum value. 
for (i in 1:ncol(data)) {
  data[,i] <- data[,i] * (1/max(data[,i]))
}

3c) To be able to test how well the model I train performs, it is necessary to keep a part of our data aside as testing data. In the following code you can easily change the size of the test data by adjusting percentage_test.

@@

@@

#Plot the predicted data vs. the original data. 
plot(test$data_raw.bp, predicted.bp[,,3])

>>>>

#Reformatting of smiles into correct format for CDK. Kekulise checks for electrons, and prevents parsing of incorrect smiles. 
parsed_smiles <- parse.smiles(data_raw$smiles, kekulise=TRUE)
#Determine which descriptors to get. 
descNames <- c(
'org.openscience.cdk.qsar.descriptors.molecular.APolDescriptor',
'org.openscience.cdk.qsar.descriptors.molecular.WienerNumbersDescriptor')
#Get descriptors
descriptors <- eval.desc(parsed_smiles, descNames)

@@

#Find all rownumbers of the values in Celcius. 
celcius <-  which(grepl('degree Celsius', data_raw$bpUnitLabel))
for (i in 1:length(celcius)) {
  #Convert the value to kelvin
  data_raw$bp[celcius[i]] <- data_raw$bp[celcius[i]] + 273.15
  #Convert the label to kelvin. 
  data_raw$bpUnitLabel[celcius[i]] <- 'kelvin'
}
#Find all rownumbers of the values in Fahrenheit. 
fahrenheit <- which(grepl('degree Fahrenheit', data_raw$bpUnitLabel))
for (i in 1:length(fahrenheit)) {
  #Convert the value to kelvin
  data_raw$bp[fahrenheit[i]] <- (data_raw$bp[fahrenheit[i]] + 459.67) * (5/9)
  #Convert the label to kelvin. 
  data_raw$bpUnitLabel[fahrenheit[i]] <- 'kelvin'
}

@@

3b) To be able to test how well the model I train performs, it is necessary to keep a part of our data aside as testing data. In the following code you can easily change the size of the test data by adjusting percentage_test.

@@

data <- data.frame(descriptors, data_raw$bp)

@@

#Plot the predicted data vs. the original data. 
plot(test$data_raw.bp, predicted.bp[,,3], xlim=c(350,1000), ylim=c(350,1000))
cor(predicted.bp[,,3], test$data_raw.bp)
